### 2013-03-11 eusflat2013/introduction.tex
I updated the part about the IKC. I'll send an email explaining my choices.

Of course, when temporal information is contained in an IS, it can be used in the querying process. Usually, querying an IS containing data representing temporal notions is done by specifying one or more time indications and requesting information that is related to these notions, where the nature and semantics of these relationships are specifically temporal. Thus, specific temporal relationships are necessary. Notably, Allen~\cite{Allen1983} presented a reasoning framework containing all semantically usefull basic temporal relationships between time intervals (and as a special case instants). The resulting basic Allen relationships are shown in figure \ref{fig:allen-relationships}.

@@

The structure of this paper is as follows: Section \ref{sec:general-preliminaries} presents some general preliminaries and naming and notation conventions used in this paper. Section \ref{sec:ikc} introduces the IKC framework and Section \ref{sec:tm} introduces the TM framework. In Section \ref{sec:proposal}, both frameworks are compared. Finally, Section \ref{sec:conclusions} presents the principal conclusions of the presented work and some possible future work.

>>>>

Of course, when temporal information is contained in an IS, it can be used in the querying process. Usually, querying an IS containing data representing temporal notions is done by specifying one or more time indications and requesting information that is related to these notions, where the nature and semantics of these relationships are specifically temporal. Thus, specific temporal relationships are necessary. Notably, Allen~\cite{Allen1983} presented a reasoning framework containing all semantically usefull basic temporal relationships between time intervals (and as a special case instants). The resulting Allen relationships are shown in figure \ref{fig:allen-relationships}.

@@

The structure of this paper is as follows: section \ref{sec:general-preliminaries} presents some general preliminaries and naming and notation conventions used in this paper. Sections \ref{sec:ikc} and \ref{sec:tm} introduce the IKC and TM frameworks respectively: both sections first introduce some preliminary concepts and techniques specific to the framework under consideration, then explain how the representation of time intervals is done and finally show how the evaluation of Allen relationships between a crisp interval and one subject to uncertainty is done. In section \ref{sec:proposal}, both frameworks are compared: first their approaches to representing time intervals are compared, next their approaches to evaluating Allen relationships are compared. Finally, section \ref{sec:conclusions} presents the principal conclusions of the presented work and some possible future work.
